\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-27 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
line 700

\begin{figure}
\begin{center}
\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
\label{fig:4testcase}
\end{center}
\end{figure}

>>>>

%\begin{figure}
%\begin{center}
%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_500.pdf}}\\[2mm]%
%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_1500.pdf}}\\[2mm]%
%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_3000.pdf}}\\[2mm]%
%\subfigure[]{\includegraphics[width=0.5\textwidth]{./Pics1/mr100_fixed/mr100_fixed_end.pdf}}%
%\caption{from top to bottom, these are screenshots taken from the test-case of MR=$100$ using fixed and unstructured mesh for the same time steps, t=500(a), t=1500(b), t=3000(c), t=end(d)}
%\label{fig:4testcase}
%\end{center}
%\end{figure}
